Automating Verification of MPC Security

### 2023-06-15 popl24/composition.tex
checkpoint

\begin{lemma}
  \label{lemma-scope}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
  and $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ then
  $(\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_2)})$
  for any $\prog_1'$ where $\flips(\prog_1') \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

@@

\begin{definition}
  We write $\owl(\prog, \{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
w  iff for all $b$ and both $w \in \{\ttt{p},\ttt{k}\}$:
  $$
  (\margd{(\condd{\progd(\prog,\be_{w})}{\{ \flip{2}{g.w} \mapsto b \}})}{\itv})(\{ \itv \mapsto b\}) = 1
  $$
\end{definition}

>>>>

\begin{lemma}
  \label{lemma-scope}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$ and
  $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ then
  $(\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_1)}) *
  (\margd{\progd(\prog_1';\prog_2)}{\iov(\prog_2)})$ for any
  $\prog_1'$ where $\prog_1';\prog_2$ is safe and $\flips(\prog_1')
  \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

\begin{definition}
  We write $g \in \prog$ iff $\view{1}{\ttt{gate:}g\ttt{tt}i} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}g\ttt{pt}i} \in \iov(\prog)$ for all $0 < i \le 4$,
  or  $\view{1}{\ttt{gate:}gi\ttt{.k}} \in \iov(\prog)$
  and $\view{1}{\ttt{gate:}gi\ttt{.p}} \in \iov(\prog)$ for all $0 < i \le 2$.
\end{definition}

\begin{lemma}
  \label{lemma-gnimo}
  If $(\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_1)}) * (\margd{\progd(\prog_1;\prog_2)}{\iov(\prog_2)})$
  and $\flips(\prog_1) \cap \flips(\prog_2) = \varnothing$ and
  $\gNIMO(\prog_1;\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$ for
  $g \in \prog_1$,
  then $\gNIMO(\prog_1';\prog_2,\{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
  for any $\prog_1'$ where $\prog_1';\prog_2$ is safe and
  $\flips(\prog_1') \cap \flips(\prog_2) = \varnothing$.
\end{lemma}

\begin{lemma}[Input Encoding]
  Given well-typed $\prog_1;E[\ttt{encode}(s_1,s_2)]$ where:
  $$
  \config{\prog_1}{E[\ttt{encode}(s_1,s_2)]} \redxs
  \config{\prog_1;\prog_2}{E[\ttt{\{ wv1 =} v_1\ttt{; wv2 = } v_2 \ttt{\}}]}
  $$
  Then:
  $$\gNIMO(\prog_1;\prog_2,v_1,s_1) \wedge \gNIMO(\prog_1;\prog_2,v_2,s_2)$$
\end{lemma}

@@

\begin{definition}
  We write $\owl(\prog, \{ \ttt{k} = \be_{\ttt{k}}; \ttt{p} = \be_{\ttt{p}}\}, g)$
 iff for all $b$ and both $w \in \{\ttt{p},\ttt{k}\}$:
  $$
  (\margd{(\condd{\progd(\prog,\be_{w})}{\{ \flip{2}{g.w} \mapsto b \}})}{\itv})(\{ \itv \mapsto b\}) = 1
  $$
\end{definition}
